\documentclass[12pt]{article}
\input{preamble.tex}

\title{Self Reflection}
\date{\today}
\author{Max Eriksson}
\onehalfspacing
\begin{document}
\maketitle

First and foremost I feel like my understanding of physics has increased during this project, mainly in this specific area, but also more generally as I read different sources. Even though the work was completely theoretical I still learned about physical and experimental realizations that are relevant to the work performed, and has thus garnered a further understanding on the experimental work as well. I also feel like I've learned how to work more independently and how to analyse and understand the results that I worked with. An important part of this was to develop a methodological approach to tackle the problem. Since the work was done analytically it was important to keep good track of the notes of the calculations.

I also think that one of the things I got better at during the project was finding relevant articles and literature to read. This I would say made me able to work more independently since I could teach my self things by finding relevant material. I would also say that I got better at reading and understanding scientific articles, especially those relevant to the work I performed. I did however, in some cases, lack sufficient mathematical knowledge to understand the proofs and derivations in some materials, although I feel that I still could understand and use the results. Furthermore, I would say that this has made me realize what I don't know, and has given me a better idea on how to further plan my education. 

One thing I think I could have done better is manage my time. Not in the sense that I did not keep deadlines, but that I tended to procrastinate a bit and then have a lot to do near the deadline. So even though I finished in time, it was more stressful than it needed to be. I think this is a consequence of getting to work so independently for the first time, and I think, and hope, that I will be better at managing my time next time. I also think it might be because I have been quite exhausted  this semester due to my studies and life in general. Furthermore, I have not had a prolonged holiday since I started university and I think that I now realize how important it is to take longer breaks and actually recover. Hopefully, I will be able to do it this summer and have more energy next semester. 

\end{document}