\section*{Acknowledgements}
First and foremost I would like to thank my supervisors, Peter and Kalle, for guiding me through this project, and providing me with invaluable understanding of the field. I want to give a special thanks to Kalle for always being available when I had any questions, and to all the discussions during those impromptu hour long meetings. I would also like to thank the rest of the division of mathematical physics, especially Peter's group, for creating a welcoming working environment and great fredagsfika.

Furthermore, I want to thank everyone who helped relieve stress during this period. Thank you, Hugo, Lukas, Fredrik, Elis, Kaspian, Kornelius, Josef, Amanda, Alma, Liam, Edvin, Herman, and all others. To all those late Wednesday nights at Pub Rydberg and the all too short weekends. To all the late night shenanigans. To Valborg and Skanör. Thank you to Tequilafredag and Utopia-eftersläppet. My gratitude goes out to Systembolaget for bringing joy to the weekends.

A special thanks is also deserved to the coffee machine at MatPhys for always providing me with much-needed caffeine. Thank you to the chair and the floor for giving me something to sit and rest on. Tack du vackra Vår för solljus och energi. Thanks to all the food I've eaten that has given me sustenance.

I want to thank all the teachers that motivated my interest for science and knowledge. For opening my eyes to the wonderful world of physics. On that note I also want to give a special thanks to Henrik, whom without I would not be here. 

Last, but certainly not least, I want to thank my family for being the reason that I am where I am today. Thank you for supporting my education and always believing in me, even when I didn't. Mamma och Pappa, tack för allt.