\section{Theoretical Framework}
\subsection{Quantum Harmonic Oscillator}
The quantum harmonic oscillator (QHO) is a quantum mechanical system useful for many applications. This stems from the fact that many systems can be approximated as harmonic close to their equilibrium position, and since the QHO is a simple system, which is possible to solve analytically it is a good starting approximation. The system has the Hamiltonian
\begin{equation}
    \hamiltonian = \frac{\pop^2}{2m} + \frac{1}{2}m\omega^2\xop^2 = \hbar\omega\left(\ad\a + \frac{1}{2}\right),
\end{equation}
where $\pop$ and $\xop$ are the momentum and position operators, $m$ is the mass of the particle, and $\omega$ is the angular frequency of the oscillator. The operators $\ad$ and $\a$ are the creation and annihilation operators, which are defined as
\begin{equation}
    \a = \sqrt{\frac{m\omega}{2\hbar}} \left(\xop + \frac{i}{m\omega} \pop\right) \quad \text{and} \quad \ad = \sqrt{\frac{m\omega}{2\hbar}} \left(\xop - \frac{i}{m\omega} \pop\right).
\end{equation}
It is also reasonable to mention the number operator $\hat{n} = \ad\a$ which has the number states, or Fock states, $\ket{n}$ as its eigenstates.

\subsection{Open Quantum Systems}
With an open quantum system we mean a quantum system which in some ways interact with an environment. This interaction could be described as a thermal coupling between the main system and some temperature bath. This will cause the system to be in a thermal equilibrium with the environment if left alone, and therefore it will be dependent on the temperature. Unless the temperature of the bath is zero, the system will be in a mixed state, described by a density matrix $\dmatrix$. Notably, if the temperature is zero, it is equivalent of considering a closed quantum system, since the coupling is thermal. \cite{Annby-Andersson:2024}

The thermal coupling will lead to dissipation of quantum information from the system to the environment. During this process, the system loses coherence. That is, the quantum mechanical properties of the system are lost and a classical description of the state becomes more appropriate. The coherence of the system is manifested in the off-diagonal elements of the density matrix. If the off-diagonal elements are zero, either by dissipation to the environment or by other means of decoherence, the system will exist in a classical probabilistic state, and any superposition of states will be lost. \cite{Annby-Andersson:2024}

The combination of the system and environment can be considered a closed system, though more complicated than the main system itself. Then by performing a partial trace over the environment a description of the system alone arises at the cost of losing information about the correlation between the two parts \cite{Annby-Andersson:2024}. This introduces an uncertainty in the state, and it is therefore necessary to treat the resulting system to be in a mixed state. If the coupling is also weak the system, after the environment has been traced over, will follow a Markovian master equation \cite{Annby-Andersson:2024}.

\subsubsection{Master Equation}
The evolution of an open quantum system can be described by a master equation, which is a differential equation and generalization of the Schrödinger equation to involve open quantum systems instead of pure states \cite{Annby-Andersson:2024}. By introducing the super operator
\begin{equation}
    \super{\hat{L}_k}\dmatrix = \hat{L}_k\dmatrix\hat{L}_k^{\dagger} - \frac{1}{2} \acomm{\hat{L}_k^\dagger \hat{L}_k}{\dmatrix},
\end{equation} 
where $\hat{L}_k$ are called Lindblad operators, the master equation on Lindblad form can be written as 
\begin{equation}
    \dt\dmatrix = -\frac{i}{\hbar}\comm{\hamiltonian}{\dmatrix} + \sum_k \gamma_k\super{\hat{L}_k}\dmatrix,
\end{equation}
where $\hamiltonian$ is the hamiltonian of the system, and $\gamma_k$ are the decay rates of the system, relating the decoherence to the environment depending on the coupling to the system \cite{Annby-Andersson:2024}. If $\gamma_k = 0$ for all $k$ the equation reduces to the von Neumann equation for a closed quantum system and the coupling to the bath is removed. The remaining term thus describes the unitary time evolution of the system and is the analogue of the Schrödinger equation for the density matrix formalism \cite{Annby-Andersson:2024}. At this stage one might also introduce the Liouvillian super operator and write the master equation more compactly as
\begin{equation}
    \dt\dmatrix = \liouvillian\dmatrix.
\end{equation}
This compactness will be useful when considering other types of perturbing effects on the system such as measurements and feedback \cite{Annby-Andersson:2024}.

For the special case considered in this thesis where the system is a QHO, the Lindblad operators can be chosen as $\hat{L}_1 = \a$ and $\hat{L}_2 = \ad$ with coefficients $\gamma_1 = \gamma(\nbar + 1)$ and $\gamma_2 = \gamma \nbar$, where $\gamma$ is a decay rate and $\nbar$ is the thermal occupation number which can be written as 
\begin{equation}
    \nbar = \frac{1}{e^{\hbar\omega/ k_\mathrm{B}T} - 1},
\end{equation}
where $T$ is the temperature of the bath and $k_\mathrm{B}$ is the Boltzmann constant \cite{Meystre:2021}. We can also note that $\hat{L}_1$ and $\gamma_1$ refer to the spontaneous emission from the system to the environment while $\hat{L}_2$ refer to spontaneous absorption from the environment to the system \cite{Meystre:2021}. Notably, for $T=0$, the thermal occupation is $\nbar = 0$ and the system will only exhibit emission and will decay.


\subsection{Continuous Measurements}
Measurement is a process which introduces decoherence in the system, and it is therefore interesting to look at its effects \cite{Jordan:2024}. The simplest view on measurements takes the form of von Neumann measurements. This type of measurement is described by a set of measurement operators which projects the system onto the eigenstates of the observable \cite{Annby-Andersson:2024}. This essentially means that all quantum information in the system is lost and full decoherence has happened. By generalizing the measurement theory one can derive what is called positive operator-valued measurement (POVM) \cite{Annby-Andersson:2024}.

Since the POVM is not necessarily a projective von Neumann measurement all coherence need not be lost after the measurement. Thus, this opens up for the possibility of performing time continuous weak measurement \cite{Annby-Andersson:2024}. To describe this type of POVM we first consider a Gaussian measurement operator
\begin{equation}
    \hat{K} = \left(\frac{2 \bar{\lambda}}{\pi}\right)^{1/4} e^{-\bar{\lambda}(z - \hat{A})^2},
\end{equation}
where $\bar{\lambda}$ represents the strength of the measurement, $z$ is a continuous outcome of the measurement, and $\hat{A}$ is the measured observable \cite{Annby-Andersson:2024}. Then by discretizing the time interval to segments of $\dd t$ and defining $\bar{\lambda} = \lambda \dd t$ we approach a situation where in the limit $\dd t \to 0$ all measurements will be weak, and the coherence of the system is minimally affected \cite{Annby-Andersson:2024}. Considering the stochastic nature of the process and averaging the possible trajectories one can derive the master equation \cite{Annby-Andersson:2024} in Lindblad form to be 
\begin{equation}
    \dt\dmatrix = \liouvillian\dmatrix + \lambda \super{\hat{A}} \dmatrix.
\end{equation}

\subsection{Feedback Control}
\subsection{Wigner Function}